---
title: A Bíblia do R
author: Michelangelo R. dos Anjos
date: '2019-04-07'
slug: a-biblia-do-r
categories:
  - R
  - Turoriais
tags:
  - R
  - Code
  - Basic
  - Tutorial
editor_options: 
  chunk_output_type: console
output:
  blogdown::html_page:
    toc: true
---

Teste :smile:

Esse post é o que eu considero o principal e mais importante do Blog. Devido a essa importância ele estará em constante atualização, pois sempre a algo novo para aprender e ensinar e esse post foi construído exatamente dessa forma, conforme as necessidades iam surgindo ao longo de todo esse tempo que utilizo o R, fui construindo um backup para ter um acesso e consultar os códigos sempre que necessário.

```{r, eval=FALSE,echo=FALSE}
#[Índice 2](#abcd)
```


```{r}
2-2

plot(density(cars$speed))

```

## Header 2

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

### Header 3
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r,eval=FALSE,echo=FALSE}
#<a name="abcd">Índice 2</a>
```
